---
title: "Exam"
params:
  number: 10
---

```{r child = here::here("fragments", "setup.qmd")}
```

```{r echo=FALSE}
library(tidyverse)
library(fontawesome)

due <- get_schedule() %>%
  mutate(assign_due = format(assign_due, format = "%b %d")) %>%
  filter(assign_n == params$number) %>%
  pull(assign_due)
due <- paste0(due, " by 11:59pm")
```

> **Due**: `r due`
>
> **Weight**: This assignment is worth 10% of your final grade.

The exam for this class is a take home exam. You will be sent exam instructions after class on December 1, and you must submit your response on Blackboard by **midnight on December 5**.

Rules:

- You must work **on your own** for this exam - you may not work with, ask questions, or otherwise collaborate with anyone else on the exam.
- You may use:
    - RStudio.
    - All class materials (slides, your notes, prior assignments, etc.)
- You may **not** use:
    - Any other resources (e.g. the internet, solution sites, etc.).
    - Other people (e.g. your classmates, people who took this class last year, etc.)
