---
title: "formr"
params:
  number: 3
  purpose: 'The purpose of this assignment is to get familiar with the [formr.org](https://formr.org/) survey platform, which we will be using to implement our surveys.'
---

<script src="https://kit.fontawesome.com/1392a7030f.js" crossorigin="anonymous"></script>

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
source(here::here("R", "settings.R"))
```

```{r child = here::here("fragments", "hw.qmd")}
```

# 1. Getting Organized

Download and edit [this template](`r url_template`) when working through this assignment. Notice that this week's template is a .Rmd file.

# 2. Readings

Next week we will start getting into designing conjoint surveys for our projects. We will implement them using [formr.org](https://formr.org/), which is an R-based platform for designing surveys. The platform allows you to use R or markdown code (just like you would in a .Rmd file) to define everything you see in an online survey. All survey elements are defined using Google Sheets.

To get familiar with the platform, go to **[this post](https://www.jhelvy.com/talks/2021-01-21-surveys-with-formr/)** on my website and watch the ~45 min video on the page. It is a recording of me introducing formr.org at a [GW Coders](https://gwcoders.github.io/) community meet up back in 2021. The first 5 minutes is a high level introduction, and the rest of the video goes into a detailed demo of the platform.

**Take notes** as you watch the video.

At the bottom of the page in the section titled "Surveys with {formr}", you can see links to the actual surveys I used in the video.

# 3. Make a practice survey

Normally I would have each team create their own account on formr.org, but at the moment the site is undergoing several upgrades and they have temporarily suspended new accounts. So, the work around for this semester will be for every team to use the same account. I will post the log in information on the class [Slack]({{< var slack >}}){target="_blank"} in the #projects channel.

For practice, try replicating the [random images](https://docs.google.com/spreadsheets/d/1hs551J6PYJNxc4sftmJyUqj6XYGYFVnN_5faQBWY7cs/edit?usp=sharing) survey I demonstrated in the video. Follow these steps:

1. Make a copy of the survey Google Sheet in GW Google Drive account. **Make sure you turn the share settings on so that anyone can view it** (if you don't, formr won't be able to read it in).
2. Log in to formr.org and create a new survey using that Google Sheet. Name your survey `practice_netID`, replacing `netID` with your `netID` (e.g. `practice_jph`).
3. Once you have your survey uploaded, you can make it live by creating a "Run". Create a new run, and give it the same name as your survey name. Add your survey to the run by clicking on the `r fa("square-pen")` icon, then add a stopping point by clicking the `r fa("stop")` icon.
4. The link to the survey will be `https://your_run_name.formr.org`. You can control whether your survey is "live" or not by modifying the "volume" icons. I recommend setting it to the `r fa("volume-down")` icon, which means people who have the link can access the survey.
5. Try it out! See if the survey works as expected. You can also click through a few times and then see the response data by going to your survey (not the run) in the formr.org admin page.

# 4. Reflect & Knit

Reflect on what you've learned while going through these readings and exercises. Is there anything that jumped out at you? Anything you found particularly interesting or confusing? After reflecting, do the following:

- Write at least a paragraph in your Rmd file.
- Click the "knit" button to compile your .Rmd file into a html web page.
- Open up the resulting reflection.html file in your web browser and see how it looks!

# 5. Submit

To submit this assignment, create a zip file of all the files in your R project folder for this assignment. Name the zip file ``r paste0('hw', params$number, '-netID.zip')``, replacing `netID` with your netID (e.g., ``r paste0('hw', params$number, '-jph.zip')``). Then copy that zip file into the "submissions" folder in your Box folder created for this class (the Box folder is named your GW netID).
