---
title: "Conjoint Surveys in formr"
params:
  number: 4
  purpose: "The purpose of this assignment is to get familiar with how to implement a conjoint survey in formr."
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
source(here::here("R", "settings.R"))
```

```{r child = here::here("fragments", "hw.qmd")}
```

# 1. Get Organized

Download and edit [this template](`r url_template`) when working through this assignment.

Then unzip the template folder (make sure you unzip it!), then open the .Rproj file to open RStudio. Open the ``r paste0('hw', params$number, '.Rmd')`` file, take notes, and write some example code as you go through the following.

# 2. Readings

Your next major team assignment is your survey plan. The central questions of your eventual survey will be your conjoint questions, which are the sets of randomized choice questions where respondents will be asked to make choices from different sets of alternatives. We have not yet gotten into all the details of how to set up those randomized questions (that will come soon!). But it is helpful at this stage to see an overview of the overall survey structure and how a conjoint survey can be built in formr.

With that in mind, read through [this blog post](https://www.jhelvy.com/posts/2021-09-18-choice-based-conjoint-surveys-in-r-with-formr/) I wrote on how to implement a choice-based conjoint survey in formr. It may not yet be immediately clear what every single piece of code is doing, but reading it at least once will help as we go forward with the class. You will probably want to use this blog post as a guide to implement your own conjoint surveys later in the class.

# 3. Reflect

Reflect on what you've learned while going through this post. Is there anything that jumped out at you? Anything you found particularly interesting or confusing? Write at least a paragraph in your ``r paste0('hw', params$number, '.Rmd')`` file. Here are some suggestions:

- Discuss some of the key insights or things you found interesting in the readings or recent class periods.
- Write about the messiest data you've seen.
- Connect the course content to your own work or project you're working on.

# 4. Knit

Click the "knit" button to compile your ``r paste0('hw', params$number, '.Rmd')`` file into a html web page. Then open the ``r paste0('hw', params$number, '.html')`` file in a web browser and proofread your report. Does all of the formatting look correct?

# 5. Submit

To submit this assignment, create a zip file of all the files in your R project folder for this assignment. Name the zip file ``r paste0('hw', params$number, '-netID.zip')``, replacing `netID` with your netID (e.g., ``r paste0('hw', params$number, '-jph.zip')``). Then copy that zip file into the "submissions" folder in your Box folder created for this class.